\subsection{Assistant Nature Manager \hfill April 2024 --- Present}
\subtext{Lausanne Employment Service, Lausanne}
\vspace{0.7\baselineskip}

Affiliation in the context of the civil service, I help with participants that need social integration. With them, we fight against invasive plants, construct birdhouses, beehotels, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Machine Learning Engineer \hfill April 2022 --- February 2024}
\subtext{Magma Learning, Lausanne}
\vspace{0.7\baselineskip}

I handled a variety of tasks, with a focus on designing, deploying, and monitoring a spaced repetition algorithm. This algorithm, based on company data, significantly improved the personalization capabilities of our application by suggesting content at optimal times to enhance user learning. Additionally, I played a key role in backend development and the seamless integration of our application into AWS, ensuring efficient database design and smooth migration of application components to the cloud.

\textit{Keywords:} Machine Learning, MLOps, NLP, TensorFlow, Keras, Software and Database Design, AWS
\vspace{0.35\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data Science Intern \hfill Sept. 2021 --- March 2022}
\subtext{Magma Learning, Lausanne}
\vspace{0.7\baselineskip}

I developed a production-ready personalized spaced repetition algorithm for the AI tutor of the company. I
designed a novel algorithm approach based on a Neural Network architecture that predicts the probability of
correctness of users on problems at any given time. Predictions can then be used to choose which problems to
reactivate to help users learn as efficiently as possible.\\

\textit{Keywords:} Recommender System, Spaced Repetition, Neural Collaborative Filtering, TensorFlow, Keras
\vspace{0.35\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Student Assistant \hfill 2020 --- 2021}
\subtext{École polytechnique fédérale de Lausanne (EPFL)}
\vspace{0.7\baselineskip}

Technical assistant, supervisor and Scrum Master for Bachelor students. This was in the context of programing courses,
one in C\texttt{++} and one in Python focusing on Data Mining and Machine Learning.

\vspace{0.35\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Student Assistant \hfill Feb. 2021 --- June 2021}
%\subtext{École polytechnique fédérale de Lausanne (EPFL)}
%\vspace{0.7\baselineskip}

%I helped the students understand the course material as well as with their coding projects. These projects focused on using
%Data Mining and Machine Learning techniques on problems using concrete real-world datasets (recommender systems,
%community detection, information retrieval, etc.). It used Python as well as distributed processing tools like Hadoop and Apache Spark.

%\vspace{0.35\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Student Assistant \hfill Sept. 2020 --- Jan. 2021}
%\subtext{École polytechnique fédérale de Lausanne (EPFL)}
%\vspace{0.7\baselineskip}

%I supervised three groups of students for their C\texttt{++} coding project. I was the Scrum Master in charge
%of the proper development of the project for each group (meetings and tasks supervision, technical assistant, etc.).

%\vspace{0.35\baselineskip}
